Journal and article coverage

### 2025-02-17 analysis/manuscript.qmd
Align with APA manual
Starting results with coverage analysis

```{r dependencies}
library(tidyverse, warn.conflicts = FALSE)
library(bigrquery)
library(kableExtra)
library(patchwork)
```

@@

As a result of the comprehensive data processing described above, datasets on open access in hybrid journals included in transformative agreements were produced for each database at country and journal level by year.
@tbl-methods_overview_tab provides a general overview of the coverage between 2019 and 2023 per database.
It shows that the majority of hybrid journals published at least one original article or review marked as core during the five-year period.
These journals formed the basis for the subsequent aggregation of publication metrics.

@@

>>>>

```{r dependencies}
library(tidyverse, warn.conflicts = FALSE)
library(bigrquery)
library(kableExtra)
library(patchwork)
library(ComplexUpset)

# Themes
my_upset_theme <-
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        plot.title.position="plot",
        plot.title = element_text(hjust = 0, vjust = 1, face = "bold"))
```

@@

As a result of the comprehensive data processing described above, datasets on open access in hybrid journals included in transformative agreements were produced for each database at country and journal level by year.
Table @tbl-methods_overview_tab provides a general overview of the coverage between 2019 and 2023 per database.
It shows that the majority of hybrid journals published at least one original article or review marked as core during the five-year period.
These journals formed the basis for the subsequent aggregation of publication metrics.

@@

First, I will present a coverage analysis. 
Then, I investigate hybrid open access uptake using the same methods for each database and the compare results against each other in order to assess the suitablility of the biblioemtric databases to examine transofrmative agreements.

## Coverage comparision

Overall, % (n = ) of hybrid journals included in transformative agreements were indexed in all three databases (Fig A).
These were followed by the combination between hoaddata and Scopus, which indexes more journals than the investiaged Web of Science collection SCIE, SSCI and the Arts & Humanities Citation Index AHCI. 
Around % of journals were only indexed by hoaddata. 
Journals

Note that there were 32 journals were indexed in WoS or Scopus.
Upon isnepction, these were due to diasmbiguity of ISSNs matching (errors ISSN).

```{r coverage_results, fig.asp=0.75}
jn_upset_articles <- readr::read_csv(here::here("data", "jn_upset_articles.csv"))
# Helper function to make text labels the same size as axis labels as seen in
# <https://wjschne.github.io/posts/making-text-labels-the-same-size-as-axis-labels-in-ggplot2/>
# Todo: Learn how to invoke it
jn_upset_articles |> group_by(Crossref, WoS, Scopus) |> summarize(across(.cols = where(is.numeric),.fns =sum, na.rm = TRUE))

ggtext_size <- function(base_size, ratio = 0.8) {
  ratio * base_size / ggplot2::.pt
}

bar_width <- 0.7
size <- get_size_mode("exclusive_intersection")

upset_overview <- ComplexUpset::upset(
  jn_upset_articles,
  c("Crossref", "WoS", "Scopus"),
  # Only journals in Crossref
  min_size = 30,
  set_sizes = FALSE,
  stripes = "transparent",
  # wrap = TRUE,
  name = "Data Source Coverage",
  base_annotations = list(
    "Journals" = (
      ComplexUpset::intersection_size(
        counts = TRUE,
        text = list(size = 8 / .pt),
        text_mapping = aes(
          label = paste0(!!upset_text_percentage(), '\n(', format(!!size, big.mark = ","), ')'),
          colour = ifelse(!!size > 5000, 'on_bar', 'on_background'),
          y = ifelse(!!size > 5000, !!size - 4000, !!size)
        ), width = bar_width
      ) +
        scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
        ggtitle("A")
    )
  ),
  annotations = list(
    "Journal size\n(log scale)" = (
      ggplot(mapping = aes(x = intersection, y = n)) +
        geom_boxplot(outliers = FALSE, width = bar_width) +
        scale_y_log10(labels =  scales::number_format(big.mark = ",")) +
        ggtitle("C")
    ),
    "Articles" = (
      ggplot(mapping = aes(y = n_cr)) +
        geom_bar(
          stat = "identity",
          color = "grey80",
          width = bar_width,
          aes(fill = "in Crossref only")
        ) +
        geom_bar(
          aes(y = doi_in_wos_and_scopus, fill = "Shared"),
          stat = "identity",
          width = bar_width,
          color = "#0093c7"
        ) +
        scale_fill_manual(
          values = c(
            `in Crossref only` = "grey80",
            `Shared` = "#0093c7"
          ),
          name = "DOI"
        ) +
        scale_y_continuous(labels =  scales::number_format(big.mark = ",")) +
        ggtitle("B")
    )
  ),
  matrix = (intersection_matrix(geom = geom_point(
    shape = "square", size = 2
  )))
)
upset_overview & my_upset_theme
```

This study compares results drawn from the openly available and regularly updated hoaddata, an R package leveraging the open scholarly data sources Crossref and OpenAlex, with the in-house database of the German Competence Network 
Overall, xxxx hybrid journals included in xxx agreements that published at least one open access article between 2019 and 2023.

### 2025-02-17 analysis/manuscript.tex
Starting results with coverage analysis

>>>>

First, I will present a coverage analysis. Then, I investigate hybrid
open access uptake using the same methods for each database and the
compare results against each other in order to assess the suitablility
of the biblioemtric databases to examine transofrmative agreements.

\subsection{Coverage comparision}\label{coverage-comparision}

Overall, \% (n = ) of hybrid journals included in transformative
agreements were indexed in all three databases (Fig A). These were
followed by the combination between hoaddata and Scopus, which indexes
more journals than the investiaged Web of Science collection SCIE, SSCI
and the Arts \& Humanities Citation Index AHCI. Around \% of journals
were only indexed by hoaddata. Journals

Note that there were 32 journals were indexed in WoS or Scopus. Upon
isnepction, these were due to diasmbiguity of ISSNs matching (errors
ISSN).

\begin{verbatim}
#> # A tibble: 7 x 10
#> # Groups:   Crossref, WoS [4]
#>   Crossref WoS   Scopus    n_cr   n_wos   n_scp       n doi_in_wos_and_scopus
#>   <lgl>    <lgl> <lgl>    <dbl>   <dbl>   <dbl>   <dbl>                 <dbl>
#> 1 FALSE    FALSE TRUE         0       0   99354   99354                 93230
#> 2 FALSE    TRUE  FALSE        0    5495       0    5495                     9
#> 3 FALSE    TRUE  TRUE         0  228954  231554  231554                225943
#> 4 TRUE     FALSE FALSE   177110       0       0  177110                   559
#> 5 TRUE     FALSE TRUE    657697       0  529707  657697                494884
#> 6 TRUE     TRUE  FALSE    10049    8919       0   10049                  1191
#> 7 TRUE     TRUE  TRUE   7313569 6477606 6469446 7313569               6161590
#> # i 2 more variables: doi_in_scopus <dbl>, doi_in_wos <dbl>
\end{verbatim}

\begin{center}
\includegraphics[width=0.99\linewidth,height=\textheight,keepaspectratio]{fig/coverage_results-1.png}
\end{center}

This study compares results drawn from the openly available and
regularly updated hoaddata, an R package leveraging the open scholarly
data sources Crossref and OpenAlex, with the in-house database of the
German Competence Network Overall, xxxx hybrid journals included in xxx
agreements that published at least one open access article between 2019
and 2023.
